Pillar 1 - Sequential Pattern Mining

### 2019-02-27 Pillar 1 - Sequential Pattern Mining.Rmd
removes previous irrelevant updata

We create a function, which, when given the code of a course, returns its title.
```{r function find_course}
find_course <- function(code){

  dataset <- d_transcript %>%
    filter(`Course ID`== code)

  title <- dataset$`Course Title`[1]

  return(title)

# Example
find_course("HUM1005")
```

@@

  data_temp <- data %>%
    arrange(
      sequenceID,
      eventID
    ) %>%
    filter(
      !is.na(eventID) # exclude courses that were never taken.
      ) %>% 
    group_by(
      sequenceID,
      eventID
    ) %>%
    summarise(
      list_item = list(unique(!!enquo(item)))
    ) %>%
    ungroup

@@

    select(
      lhs, rhs,
      support, count,
      confidence,
      matches("rhsTake.support"),
      lift,
      matches("rhsTake.count")
      ) %>%

@@

```{r show rules}
print(AR$THL)
print(SR$THL)
```

>>>>

@@

  data_temp <- data %>%
    arrange(
      sequenceID,
      eventID
    ) %>%
    filter(
      !is.na(eventID) # exclude courses that were never taken.
      ) %>%

    group_by(
      sequenceID,
      eventID
    ) %>%
    summarise(
      list_item = list(unique(!!enquo(item)))
    ) %>%
    ungroup

@@

    select(
      lhs, rhs,
      matches("rhsTake.count"), count,
      matches("rhsTake.support"),
      confidence,
      support, 
      lift
      ) %>%

@@

```{r show rules}
print(AR_rulesAPP$THL)
print(SR_rulesAPP$THL)
```
